Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-04-23 paper.tex
Add reference for Re effects on dynamic stall
Add to conclusions regarding XFOIL calculations

Bousman showed that dynamic stall was insensitive to Reynolds number for $Re=1.0
\times 10^5$--$2.5 \times 10^5$ \cite{Bousman2000-evaluation}.

@@

If using scaled physical models to predict array performance, it is important to
keep all turbines in the linear regime to avoid exaggerated power deficiencies
for downstream turbines, despite similarities in wake characteristics. These
results also suggest that low Reynolds number physical model stydies of turbine
arrays may see exaggerated levels of wake recovery, leading to inadequate or
inappropriate spacing or layouts.

>>>>

Bousman showed that dynamic stall was insensitive to Reynolds number for $Re=1.0
\times 10^5$--$2.5 \times 10^5$ \cite{Bousman2000-evaluation}, Though Singleton
and Yeager Jr. state that Reynolds number effects on dynamics stall remains an
unsolved question \cite{Singleton2000}.

@@

We propose a method for predicting Reynolds number dependence of a cross-flow
turbine using static airfoil characteristics and turbine blade kinematics. It is
shown that the peak torque coefficient computed this way shows similar Reynolds
number sensitivity---a better predictor than conventional quantifications of
airfoil performance, e.g., lift-to-drag ratio. Is it also shown from this metric
that foils with higher camber are more Reynolds number dependent but have
smaller slopes in the linear regime.

If using scaled physical models to predict array performance, it is important to
keep all turbines in the linear regime to avoid exaggerated power deficiencies
for downstream turbines, despite similarities in wake characteristics. These
results also suggest that low Reynolds number physical model studies of turbine
arrays may see exaggerated levels of wake recovery, leading to inadequate or
inappropriate spacing or layouts.
